Measurement of a dwarf galaxy rotational velocity from its Lyman-alpha line emission

### 2016-06-16 paper/letter.tex
letter includes new plot with multiphase and rotation

\begin{figure}
\begin{center}
\includegraphics[width=0.8\textwidth]{tolfit.pdf}
\caption{{\bf Symmetric triple peaked Ly-$\alpha$ emission of \tol.}
  Dots correspond to the observational data. The line shows the result
of our best model from a full radiative transfer simulation. The best
parameters correspond to a rotational velocity of $300$km s$^{-1}$,
neutral Hydrogen optical depth of $10^{7}$ and a viewing angle of
$65^{\circ}$ measured from the rotation axis.} 
\end{center}
\end{figure}

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=0.8\textwidth]{CLARA-TOL-main.pdf}
\caption{{\bf Broadn, single peaked and symmetric Ly-$\alpha$ emission of \tol.}
  Dots correspond to the observational data. The line shows the results
of our best model from a full radiative transfer simulation both for the rotation and multiphase models.}
\end{center}
\end{figure}
